Combat Sandbox

### 2023-10-11 combat_sandbox.Rmd
fixed combat errs by using model.matrix to create covar matrix

#covariates
covar.mat <- ukb_df_sites %>%
  dplyr::select(c(age_days, sex)) %>%
  mutate(age_days = as.numeric(age_days)) %>%
  as.matrix()
#weirdly converts age_days to a character, idk if that will be a problem

@@

simple combat with linear model for covariates
```{r}
cf.lm <- comfam(rvol.df, batch, covar.mat, lm, formula = y ~ age_days + sex)
```

Getting warning - Warning: prediction from a rank-deficient fit may be misleading

combat with age as smooth
```{r}
cf.gam <- comfam(rvol.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sex)
```

>>>>

#covariates - using model.matrix to dummycode sex as numeric
covar.mat <- model.matrix( ~ age_days + sex, data=ukb_df_sites)

@@

simple combat with linear model for covariates
```{r}
cf.lm <- comfam(rvol.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale)
```

combat with age as smooth
```{r}
cf.gam <- comfam(rvol.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale)
```
